Constructing a universe for the setoid model

### 2020-06-29 paper.tex
Added footnote on functorial model conostruction PoV.

The setoid model presented in the previous section is peculiar in several
ways. One is that it can be presented in a very small type theoretic
metatheory. The other important aspect is that it is \emph{strict}, namely every
equation of the original syntax holds by definition in the semantics. One
advantage of strict models is that they can be turned into \emph{syntactic
  translations}, in which syntactic objects of the source theory are interpreted
as their counterparts in another \emph{target} theory. In the case of the setoid
model, this gives rise to a \emph{setoid translation}, where source contexts are
interpreted as target contexts together with a target type representing the
equivalence relation, and so on. \todo{maybe expand this?}

>>>>

The setoid model presented in the previous section is peculiar in several
ways. One is that it can be presented in a very small type theoretic
metatheory. The other important aspect is that it is \emph{strict}, namely every
equation of the original syntax holds by definition in the semantics. One
advantage of strict models is that they can be turned into \emph{syntactic
  translations}, in which syntactic objects of the source theory are interpreted
as their counterparts in another \emph{target} theory. In the case of the setoid
model, this gives rise to a \emph{setoid translation}, where source contexts are
interpreted as target contexts together with a target type representing the
equivalence relation, and so on.\todo{maybe expand this?}%
\footnote{%
Semantically, this translation corresponds to a model construction, in particular a functor from the category of models of the target theory to the category of models of what will be Setoid Type Theory.
Since the setoid translation is structural in the context component, we can work with models in the style of categories with families rather than contextual categories.
}
